### 2016-05-19 2016-lrec-tyvmorph/poster.tex
pdf of latex poster
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68629 72bbbca6-d526-0410-a7d9-f06f51895060

		\headerbox{Further information}{name=getting,column=0,below=development,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (8in, 0.04in) {
				{\huge Thanks!}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: {\Large \url{http://turkic.apertium.org/}} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}

>>>>

		\headerbox{Further information}{name=getting,column=0,below=development,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (6.75in, 0.04in) {
				\parbox{3in}{
				\centering
				{\huge \textbf{Четтирдивис!}}\\
				\texttt{четтир\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{pl}}\vspace{1em}\\
				{\Large \url{http://turkic.apertium.org/}}
				}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: \url{http://turkic.apertium.org/} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}
